### 2021-08-25 A methodological framework to enable the roaming agreement digitization: An NLP-based approach/paper.tex
25.08.21.6

In order to standardize technical, commercial and legal aspects of RA, the GSM Association broadly outlines the content of such RA in standardized form for its members \cite{b2}. Reference \cite{b3} provides a list of the most commonly used GSMA standards, which are summarized bellow: (1) AA.12 constitutes a standard GSMA or Permanent Reference Document; (2) AA.13 contains the common annexes with operational information (e.g., information on tap file, billing data, settlement procedure, customer care, fraud, etc.); (3) AA.14 involves the individual annexes containing information about the operator (e.g., contact details of the roaming team, fraud team, IREG team, TADIG team, etc.) and (4) AA.19 is an addendum to the international RA to determine specific properties such as charging, billing and accounting for a specific scenario such as SMS interworking. Thus, the contractual relationship between MNOs depends on the drafting of an RA between the parties.

@@

\section{NLP Engine methodology}
Overall, the logic designed for the NLP engine follows two approaches: detection and comparison. Detection represents the capability to locate \textit{variables} in a text file, i.e., the Roaming Agreement. Comparison represents the capacity to find \textit{similarities} and differences between the sub-articles present in the Roaming Agreement with respect to the sub-articles present in the GSMA standard template. For example, while an almost total coincidence between texts at the sub-article level represents a \textit{standard clause}, an almost null coincidence between texts (or simply the non-existence of a sub-article of the GSMA standard template in the Roaming Agreement) represents a \textit{customized text}. Thus, the intermediate case is represented by the \textit{variation} in which there is a high coincidence between sub-articles and the existing differences are given by the presence of \textit{variables} such as the name of the MNO and the start date of the agreement. The technologies that enable both detection and comparison are discussed below as part of the \textit{background}.

\subsection{Amazon comprehend}\label{AA}
Define abbreviations and acronyms the first time they are used in the text

\subsection{Similarity Analysis}
Define abbreviations and acronyms the first time they are used in the text

@@

\bibitem{b3} ROCCO, “The International Roaming Agreement,” 2017.

\bibitem{b4} ROCCO, “What is ROAMING HUBBING?,” 2017.

@@

>>>>

In order to standardize technical, commercial and legal aspects of RA, the GSM Association broadly outlines the content of such RA in standardized form for its members \cite{b2}. Reference \cite{b3} provides a list of the most commonly used GSMA standards, which are summarized bellow: (1) AA.12 constitutes a standard GSMA or Permanent Reference Document; (2) AA.13 contains the common annexes with operational information (e.g., information on tap file, billing data, settlement procedure, customer care, fraud, etc.) and (3) AA.14 involves the individual annexes containing information about the operator (e.g., contact details of the roaming team, fraud team, IREG team, TADIG team, etc.).

@@

\section{NLP Engine methodology}
Overall, the logic designed for the NLP engine follows two approaches: detection and comparison. Detection represents the capability to locate \textit{variables} in a text file, i.e., the Roaming Agreement. Comparison represents the capacity to find \textit{similarities} and differences between the sub-articles present in the Roaming Agreement with respect to the sub-articles present in the GSMA standard template. For example, while an almost total coincidence between texts at the sub-article level represents a \textit{standard clause}, an almost null coincidence between texts (or simply the non-existence of a sub-article of the GSMA standard template in the Roaming Agreement) represents a \textit{customized text}. Thus, the intermediate case is represented by the \textit{variation} in which there is a high coincidence between sub-articles and the existing differences are given by the presence of \textit{variables} such as the name of the MNO and the start date of the agreement. The technologies that enable both detection and comparison are discussed below as part of the \textit{background}. The third section integrates these tools as part of the designed methodology.

\subsection{Amazon comprehend}
In short, \textit{Amazon Comprehend} is a service that uses NLP techniques to extract insights about the content document by recognizing  the  entities,  key  phrases,  language,  sentiments,  and  other  common  elements  in  a  text \cite{b11}. The capabilities that \textit{Amazon Comprehend} integrates are key to the \textit{detection} approach.

\subsection{Similarity Analysis}
Similarity is used to compare different types of data, so it is a resource used for pattern classification, clustering and information retrieval problems \cite{b12}. Therefore, the similarity falls within the comparison approach. In this regard, our work distinguishes between two types of similarities: Jaccard similarity and Cosine similarity \cite{b13}. While the first one is established as the size of the intersection divided by the size of the union of two sets, the second one implies the determination of the cosine of the angle between two vectors.

@@

\bibitem{b3} ROCCO, “The International Roaming Agreement,” 2017. [Online]. Available: https://www.roccoresearch.com/portfolio-items/the-roaming-agreement/. [Accessed: 24-Ago-2021].

\bibitem{b4} ROCCO, “What is ROAMING HUBBING?,” 2017. [Online]. Available: https://www.roccoresearch.com/portfolio-items/roaming-hubbing/. [Accessed: 24-Ago-2021].

@@

\bibitem{b11} AWS, “Amazon Comprehend Developer Guide,” 2021. [Online]. Available: https://docs.aws.amazon.com/comprehend/latest/dg/comprehend-dg.pdf. [Accessed: 24-Jul-2021].

\bibitem{b12} J. Santisteban and J. Tejada-Cárcamo, "Unilateral Weighted Jaccard Coefficient for NLP," 2015 Fourteenth Mexican International Conference on Artificial Intelligence (MICAI), 2015, pp. 14-20, doi: 10.1109/MICAI.2015.9.

 \bibitem{b13} S. Gupta, “Overview of Text Similarity Metrics in Python,” May 15, 2018, 2018. [Online]. Available: https://towardsdatascience.com/overview-of-text-similarity-metrics-3397c4601f50. [Accessed: 25-Jul-2021].
